Why is time-to-resistance in mixtures influenced differently by effectiveness and exposure ?

### 2016-12-09 inst/documents/effectiveness_exposure_difference.Rmd
typo
increase 2x2 plot size
nice 4 panel fig with labels working

scaneario exploration :

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=5, fig.show='hold', fig.align='left', fig.cap="test A.  B. C. D."}

@@

layout(matrix(1:4,2,2, byrow = TRUE))
#effectiveness on mixture

#plot margins
oldpar <- par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#base scenario
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

@@

par(oldpar)

@@

>>>>

scenario exploration :

@@

```{r, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="test A.  B. C. D."}

@@

#layout(matrix(1:4,2,2, byrow = TRUE))
#add lower panel for legend
#layout(matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.5), respect=FALSE)

# layout( matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )

#layout.show(n=5)

# layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.2,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )

layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

#effectiveness on mixture

#testing
# plot(1)
# plot(1)
# plot(1)
# plot(1)

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.5', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

#base scenario

par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','m','a','m'), xlabs = FALSE, cex.axis = 0.6, addLegend=FALSE, main='', maxX = 120 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure: 0.8', line= -2, side=2, cex=0.8) #side=1b,2l,3t,4r

@@

#adding legend in lower panel
#plot margins
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)

plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')

legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.5', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1: 0.8', line= -2, side=1, cex=0.8) #side=1b,2l,3t,4r

@@

<!-- par(mar=c(0, 0, 0, 0)) -->
<!-- layout( matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.3),  -->
<!-- respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) ) -->

<!-- #layout.show(n=5) -->

<!-- plot(1) -->
<!-- plot(1) -->
<!-- plot(1) -->
<!-- plot(1) -->

<!-- #dev.new(height=5,width=10) -->
<!-- plot( 0, type="n", axes=TRUE, ann=FALSE, pty='m', fin=c(5,1)) #par("din"))  -->

<!-- legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE ) -->

<!-- par(oldpar) -->
